working owls methods

### 2020-11-04 manuscript_working/ms_working_RMD.Rmd
broadcast results wrt detection

The broadcast species were consistent at each station across years, but varied by route. For stations $j = 1, 2, \ldots, 10$ at routes EI1, EI2, M2, N1, and N2, the following broadcast species were used, respectively: Pacific, Mottled, Crested, Black and White, Spectacled, Mottled, Crested, Black and White, and Spectacled. At the route M1, the following species were called at stations $j = 1, 2, \ldots, 10$, respectively: Whiskered, Mottled, Gaut Barred, Stygian, Great Horned, Whiskered, Mottled, Gaut Barred, Stygian, and Great Horned. Thus, the effective sample sizes of the different broadcast species varied.

>>>>

The broadcast species were consistent at each station across years, but varied by route. For stations $j = 1, 2, \ldots, 10$ at El Imposible and Nancachaname, the following broadcast species were used, respectively: Pacific, Mottled, Crested, Black and White, Spectacled, Mottled, Crested, Black and White, and Spectacled. At Montecristo, the following species were called at stations $j = 1, 2, \ldots, 10$, respectively: Whiskered, Mottled, Gaut Barred, Stygian, Great Horned, Whiskered, Mottled, Gaut Barred, Stygian, and Great Horned. Thus, the effective sample sizes of the different broadcast species varied.
